Analysis paper

### 2021-05-24 analysis/analysis.Rmd
add absolute error distribution plot

@@

@@

@@

>>>>

p_combined_ae <- distribution_plot_wis(df = scores, 
                                        x = "aem") +
  facet_wrap(~ target_type, ncol = 1, scales = "free_x")

@@

p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free_x")

@@

p_phases_ae <- distribution_plot_wis(df = scores, x = "aem") + 
  facet_wrap( ~ target_phase, scales = "free_x")

@@

pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

pl_ae
ggsave("plots/distribution_scores_ae.png")
